
# Hello Friends: I am not known for making beauftiful files. So feel free if you are bored.

```{r}

load("/home/angelo/Documents/Uni/Courses/Machine Learning & Algorithms/group_assignment/data/bookings_train.RData")
library("tidymodels")
library("themis")
library("knitr")
library("ranger")
library("doParallel")
library("vip")
library("skimr")
library("corrplot")
library("ggridges")
library("forcats")

require("lubridate")

load("/home/angelo/Documents/Uni/Courses/Machine Learning & Algorithms/group_assignment/data/bookings_test.RData")

```


```{r}
# convert to day of week 
tst <- c(bookings_train$arrival_date_month)
bookings_train$arrival_date_month_numb <- match(tst,month.name)

bookings_train$date_col <- as.Date(ISOdate(year = bookings_train$arrival_date_year, month = bookings_train$arrival_date_month_numb, day = bookings_train$arrival_date_day_of_month))

bookings_train$arrival_date_day_of_week <- wday(bookings_train$date_col)

bookings_train$arrival_date_day_of_week <- as.factor(bookings_train$arrival_date_day_of_week)



# reserved roomtype being equal 
bookings_train$got_reserved_room <- as.numeric(bookings_train$reserved_room_type == bookings_train$assigned_room_type)

bookings_train$got_reserved_room <- as.factor(bookings_train$got_reserved_room)


```

```{r}
bookings_train$reserved_room_type <- ifelse(bookings_train$reserved_room_type == "L", "I", bookings_train$reserved_room_type)
```


```{r}
# here we replace the null values with NA! 
bookings_train$country <- ifelse(bookings_train$country == "NULL", NA, bookings_train$country)

```



## Observe proportions in the original outcome
```{r}
bookings_train |> count(is_cancelled) |> 
  mutate(prop = n / sum(n))
bookings_train |> group_by(is_cancelled)|> knit_print()

```



```{r}
skim(bookings_train) |> group_by("is_cancelled") |> knit_print()
```





```{r}
# convert to factor 
bookings_train$arrival_date_year <- as.factor(bookings_train$arrival_date_year)
bookings_train$arrival_date_month <- as.factor(bookings_train$arrival_date_month)
bookings_train$arrival_date_week_number <- as.factor(bookings_train$arrival_date_week_number)
bookings_train$arrival_date_day_of_month <- as.factor(bookings_train$arrival_date_day_of_month)
bookings_train$reserved_room_type <- as.factor(bookings_train$reserved_room_type)
bookings_train$assigned_room_type <- as.factor(bookings_train$assigned_room_type)
bookings_train$country <- as.factor(bookings_train$country)

bookings_train$arrival_date_day_of_week <- as.numeric(bookings_train$arrival_date_day_of_week)
bookings_train$arrival_date_month_numb <- as.numeric(bookings_train$arrival_date_month_numb)
bookings_train$arrival_date_week_number <- as.numeric(bookings_train$arrival_date_week_number)

```







# Simple preprocsessing
```{r}
bookings_train$country <- fct_lump_min(as.factor(bookings_train$country), min=300, other_level = "Other")

# remove 0 visits
bookings_train <- bookings_train %>% 
  filter(!(stays_in_weekend_nights == 0 & stays_in_week_nights == 0))

bookings_train <- bookings_train %>% 
  filter(!(stays_in_weekend_nights == 0 & stays_in_week_nights == 0)) %>% 
  filter(adults != 0)



bookings_train <- bookings_train %>% 
  filter(!(adr < 0))

```

```{r}

bookings_train$total_visitors <- bookings_train$children + bookings_train$adults + bookings_train$babies

```

```{r}
# split the data
set.seed(42)
bookings_train_split <- initial_split(data = bookings_train, prop = 0.80, 
                          strata = is_cancelled)

# I keep the train in the name for a reason: this way we can differentiate between validation and test set later on
bookings_train_train <- training(bookings_train_split)
bookings_train_test <- testing(bookings_train_split)
print(bookings_train_train |> count(is_cancelled) |> 
  mutate(prop = n / sum(n)))
print(bookings_train_test |> count(is_cancelled) |> 
  mutate(prop = n / sum(n)))

```

# Preprocessing reciepe

```{r}

recipe_prelim <- recipe(is_cancelled ~ ., data = bookings_train_train) |> 
  update_role( "date_col", "arrival_date_month", "arrival_date_day_of_month", "children","assigned_room_type", "reserved_room_type", "arrival_date_week_number", "total_visitors", new_role = "metadata") |>
  step_other("reserved_room_type", "meal" , "market_segment") |>
  step_harmonic('arrival_date_day_of_week',frequency=1,cycle_size=7, role='predictor') |>
 # step_harmonic('arrival_date_week_number',frequency=1,cycle_size=53, role='predictor') |>
  # step_harmonic('arrival_date_month_numb',frequency=1,cycle_size=12, role='predictor') |>   
  step_impute_mode("country") |>
  step_normalize(all_numeric_predictors())|>
  step_dummy(all_nominal_predictors())|>
  # step_impute_knn(all_numeric_predictors()) |>
  step_nzv() |>
  step_downsample("is_cancelled")



```




```{r}
set.seed(82001)
cv_folds <- bookings_train_train |> vfold_cv(v = 3, strata = is_cancelled)
```

# Random Forst
```{r}
rf_model_tune <- rand_forest(mtry = tune(), trees = 500) |>
  set_mode("classification") |>
  set_engine("ranger")
```

### da workflows
```{r}
rf_tune_wf <- workflow() |> 
  add_recipe(recipe_prelim) |> 
  add_model(rf_model_tune)


```

# metrics
```{r}
class_metrics <- metric_set(accuracy, f_meas,bal_accuracy, kap, sensitivity, 
                            specificity, roc_auc, precision)
```

# Random forest model

```{r}
registerDoParallel()

set.seed(42)
# as I said: i am a basic 42-bitch
rf_tune_res <- tune_grid(
  rf_tune_wf,
  resamples = cv_folds,
  grid = tibble(mtry = 7:12),
  metrics = class_metrics
)

show_notes(.Last.tune.result)
```


```{r}
rf_tune_res |>
  collect_metrics()
```



```{r}
rf_tune_res |>
  collect_metrics() |>
  filter(.metric %in% c("sensitivity", "specificity")) |>
  ggplot(aes(x = mtry, y = mean, ymin = mean - std_err, ymax = mean + std_err, 
             colour = .metric)) +
  geom_errorbar() + 
  geom_line() +
  geom_point() +
  facet_grid(.metric ~ ., scales = "free_y") 
```





```{r}
rf_tune_res |>
  collect_metrics() |>
  filter(.metric %in% c("roc_auc", "accuracy", "kap")) |>
  ggplot(aes(x = mtry, y = mean, ymin = mean - std_err, ymax = mean + std_err, 
             colour = .metric)) +
  geom_errorbar() + 
  geom_line() +
  geom_point() +
  facet_grid(.metric ~ ., scales = "free_y") 
```
# Test set performance

```{r}
best_acc <- select_best(rf_tune_res, "accuracy")
rf_final_wf <- finalize_workflow(rf_tune_wf, best_acc)
rf_final_wf
```


# random forstest
```{r}
set.seed(9923)
rf_final_fit <- rf_final_wf |>
  last_fit(bookings_train_split, metrics = class_metrics)
# The results on the test set for class predictions are:
rf_final_fit |>
  collect_metrics()
```


Confusion matrix and visual assessments of performance
```{r}
# rf_final_fit |> collect_predictions() |> 
#   conf_mat(truth = is_cancelled, estimate = .pred_class) 
# # As one would expect, there are many more false positives than false negatives.
```

Here are some visualizations for the test set predictions. The ROC-curve can be constructed as follows:
```{r}
# rf_final_fit |> collect_predictions() |> 
#   roc_curve(is_cancelled, .pred_Class) |> 
#   autoplot()
```

There is clearly room for improvement in terms of AUC. The lift curve look as follows:
```{r}
# rf_final_fit |> collect_predictions() |> 
#   lift_curve(loan_status, .pred_Default) |> 
#   autoplot()
#' So when targeting the 25% of loans with the highest predicted probability of default, a bit less than twice as many loans that defaulted are identified compared to when targeting is done randomly.
```

Finally, here is a gain chart:
```{r}
# rf_final_fit |> collect_predictions() |> 
#   gain_curve(loan_status, .pred_Default) |> 
#   autoplot()
```



























