---
title: "Testset_Evaluation"
author: "Myself"
date: "2022-12-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Imports
```{r}
library("tidymodels")
library("themis")
library("knitr")
library("ranger")
library("doParallel")
library("vip")
library("skimr")
library("corrplot")
library("ggridges")
library("forcats")
library("vip")
library("bonsai")
library("lightgbm")
library("xgboost")

require("lubridate")

```

## Load Train and Test Data
```{r}
load("D:/Universiteit/R/GroupAssignmentML2022/bookings_train.RData")
load("D:/Universiteit/R/GroupAssignmentML2022/bookings_test_solutions.RData")
```


## Feature Engineering on Train- & Test data
```{r}
# Create Day of Week: Train
tst <- c(bookings_train$arrival_date_month)
bookings_train$arrival_date_month_numb <- match(tst,month.name)

bookings_train$date_col <- as.Date(ISOdate(year = bookings_train$arrival_date_year, month = bookings_train$arrival_date_month_numb, day = bookings_train$arrival_date_day_of_month))

bookings_train$arrival_date_day_of_week <- wday(bookings_train$date_col)

bookings_train$arrival_date_day_of_week <- as.factor(bookings_train$arrival_date_day_of_week)



# Create Day of Week: Test
tst <- c(bookings_test_solutions$arrival_date_month)
bookings_test_solutions$arrival_date_month_numb <- match(tst,month.name)

bookings_test_solutions$date_col <- as.Date(ISOdate(year = bookings_test_solutions$arrival_date_year, month = bookings_test_solutions$arrival_date_month_numb, day = bookings_test_solutions$arrival_date_day_of_month))

bookings_test_solutions$arrival_date_day_of_week <- wday(bookings_test_solutions$date_col)

bookings_test_solutions$arrival_date_day_of_week <- as.factor(bookings_test_solutions$arrival_date_day_of_week)



# Did Customer get assigned their reserved Room?: Train
bookings_train$got_reserved_room <- as.numeric(bookings_train$reserved_room_type == bookings_train$assigned_room_type)

bookings_train$got_reserved_room <- as.factor(bookings_train$got_reserved_room)



# Did Customer get assigned their reserved Room?: Test
bookings_test_solutions$got_reserved_room <- as.numeric(bookings_test_solutions$reserved_room_type == bookings_test_solutions$assigned_room_type)

bookings_test_solutions$got_reserved_room <- as.factor(bookings_test_solutions$got_reserved_room)




# Total Visitors: Train
bookings_train$total_visitors <- bookings_train$children + bookings_train$adults + bookings_train$babies


# Total Visitors: Test
bookings_test_solutions$total_visitors <- bookings_test_solutions$children + bookings_test_solutions$adults + bookings_test_solutions$babies
```


## Data Cleaning
```{r}
# Set Country NULL values to NA: Train
bookings_train$country <- ifelse(bookings_train$country == "NULL", NA, bookings_train$country)

# convert to factor: Train 
bookings_train$arrival_date_year <- as.factor(bookings_train$arrival_date_year)
bookings_train$arrival_date_month <- as.factor(bookings_train$arrival_date_month)
bookings_train$arrival_date_week_number <- as.factor(bookings_train$arrival_date_week_number)
bookings_train$arrival_date_day_of_month <- as.factor(bookings_train$arrival_date_day_of_month)
bookings_train$reserved_room_type <- as.factor(bookings_train$reserved_room_type)
bookings_train$country <- as.factor(bookings_train$country)

bookings_train$arrival_date_day_of_week <- as.numeric(bookings_train$arrival_date_day_of_week)
bookings_train$arrival_date_month_numb <- as.numeric(bookings_train$arrival_date_month_numb)
bookings_train$arrival_date_week_number <- as.numeric(bookings_train$arrival_date_week_number)

bookings_train$country <- fct_lump_min(as.factor(bookings_train$country), min=200, other_level = "Other")



# Set Country NULL values to NA: Test
bookings_test_solutions$country <- ifelse(bookings_test_solutions$country == "NULL", NA, bookings_test_solutions$country)

# convert to factor: Test
bookings_test_solutions$arrival_date_year <- as.factor(bookings_test_solutions$arrival_date_year)
bookings_test_solutions$arrival_date_month <- as.factor(bookings_test_solutions$arrival_date_month)
bookings_test_solutions$arrival_date_week_number <- as.factor(bookings_test_solutions$arrival_date_week_number)
bookings_test_solutions$arrival_date_day_of_month <- as.factor(bookings_test_solutions$arrival_date_day_of_month)
bookings_test_solutions$reserved_room_type <- as.factor(bookings_test_solutions$reserved_room_type)
bookings_test_solutions$country <- as.factor(bookings_test_solutions$country)

bookings_test_solutions$arrival_date_day_of_week <- as.numeric(bookings_test_solutions$arrival_date_day_of_week)
bookings_test_solutions$arrival_date_month_numb <- as.numeric(bookings_test_solutions$arrival_date_month_numb)
bookings_test_solutions$arrival_date_week_number <- as.numeric(bookings_test_solutions$arrival_date_week_number)

bookings_test_solutions$country <- fct_lump_min(as.factor(bookings_test_solutions$country), min=200, other_level = "Other")
```


## Remove Seemingly wrong Observations (TRAIN SET ONLY!!! -- DO NOT TOUCH TEST SET)
```{r}
# remove 0 visits
bookings_train <- bookings_train %>% 
  filter(!(stays_in_weekend_nights == 0 & stays_in_week_nights == 0)) %>% 
  filter(adults != 0) %>% 
  filter(!(adr < 0))

```


## Define Recipe
```{r}
recipe_prelim <- recipe(is_cancelled ~ ., data = bookings_train) |> 
    step_novel('assigned_room_type') |>
  update_role( "date_col", "arrival_date_month", "babies",  "arrival_date_day_of_month", "days_in_waiting_list", new_role = "metadata") |>
  step_harmonic('arrival_date_week_number',frequency=1,cycle_size=53, role='predictor') |>
  step_harmonic('arrival_date_month_numb',frequency=1,cycle_size=12, role='predictor') |>   
  step_harmonic('arrival_date_day_of_week',frequency=1,cycle_size=7, role='predictor') |>   
  step_impute_mode("country") |>
  step_normalize(all_numeric_predictors())|>
  step_dummy(all_nominal_predictors())|>
  step_downsample("is_cancelled")
```


## Define LightGBM
```{r}
lgbm_model <- boost_tree(
  mtry = 9, 
  trees = 2124, 
  min_n = 4, 
  tree_depth = 10,
  learn_rate = 0.009549070,
  stop_iter = 300)|>
  set_mode("classification") |>
set_engine("lightgbm")
```


## Define Random Forest
```{r}
rf_model <- rand_forest(mtry = 9, 
                        trees = 500) |>
  set_mode("classification") |>
  set_engine("ranger", importance = "permutation")
```


## Define XGBoost
```{r}
xgb_model <- 
  boost_tree(trees = 1626, 
             tree_depth = 10, 
             learn_rate = 0.0055,
             mtry = 9, 
             min_n = 7, 
             stop_iter = 400) |>
  set_mode("classification") |>
set_engine("xgboost")
```

## Define Linear Model
```{r}
lm_model <- logistic_reg(mode = "classification", 
                       engine = "glm", 
                       penalty = NULL, 
                       mixture = NULL)
```


## Workflow LightGBM
```{r}
lgbm_wf <- workflow() |>
  add_recipe(recipe_prelim) |>
  add_model(lgbm_model)
```

## Workflow Random Forest
```{r}
rf_wf <- workflow() |>
  add_recipe(recipe_prelim) |>
  add_model(rf_model)
```

## Workflow xGBoost
```{r}
xgb_wf <- workflow() |>
  add_recipe(recipe_prelim) |>
  add_model(xgb_model)
```

## Workflow Linear Model
```{r}
lm_wf <- workflow() |>
  add_recipe(recipe_prelim) |>
  add_model(lm_model)
```

## Fit LightGBM
```{r}
set.seed(42)

lgbm_wf_fit <- lgbm_wf %>% 
  fit(data = bookings_train)
```

## Fit Random Forest
```{r}
set.seed(42)

rf_wf_fit <- rf_wf %>% 
  fit(data = bookings_train)
```

## Fit XGBoost
```{r}
set.seed(42)

xgb_wf_fit <- xgb_wf %>% 
  fit(data = bookings_train)
```

## Fit Linear Model
```{r}
set.seed(42)

lm_wf_fit <- lm_wf %>% 
  fit(data = bookings_train)
```


## Define Evaluation Metrics
```{r}
eval_metrics <- metric_set(accuracy, bal_accuracy, recall, precision, f_meas, specificity)
```


## LightGBM: Predict on the Test Set
```{r}
lgbm_results <- bookings_test_solutions %>% select(is_cancelled) %>% 
  bind_cols(lgbm_wf_fit %>% 
              predict(new_data = bookings_test_solutions)) %>% 
  bind_cols(lgbm_wf_fit %>% 
              predict(new_data = bookings_test_solutions, type = "prob"))

```

## Random Forest: Predict on the Test Set
```{r}
rf_results <- bookings_test_solutions %>% select(is_cancelled) %>% 
  bind_cols(rf_wf_fit %>% 
              predict(new_data = bookings_test_solutions)) %>% 
  bind_cols(rf_wf_fit %>% 
              predict(new_data = bookings_test_solutions, type = "prob"))

```

## XGBoost: Predict on the Test Set
```{r}
xgb_results <- bookings_test_solutions %>% select(is_cancelled) %>% 
  bind_cols(xgb_wf_fit %>% 
              predict(new_data = bookings_test_solutions)) %>% 
  bind_cols(xgb_wf_fit %>% 
              predict(new_data = bookings_test_solutions, type = "prob"))

```


## Linear Model: Predict on the Test Set
```{r}
lm_results <- bookings_test_solutions %>% select(is_cancelled) %>% 
  bind_cols(lm_wf_fit %>% 
              predict(new_data = bookings_test_solutions)) %>% 
  bind_cols(lm_wf_fit %>% 
              predict(new_data = bookings_test_solutions, type = "prob"))

```


# LightGBM: Evaluation Metrics
```{r}
eval_metrics(data = lgbm_results, truth = is_cancelled, estimate = .pred_class)
```

# Random Forest: Evaluation Metrics
```{r}
eval_metrics(data = rf_results, truth = is_cancelled, estimate = .pred_class)
```

# XGBoost: Evaluation Metrics
```{r}
eval_metrics(data = xgb_results, truth = is_cancelled, estimate = .pred_class)
```

# Logistic Model: Evaluation Metrics
```{r}
eval_metrics(data = lm_results, truth = is_cancelled, estimate = .pred_class)
```






