---
title: "Testset_Evaluation"
author: "Myself"
date: "2022-12-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Imports
```{r}
library("tidymodels")
library("themis")
library("knitr")
library("ranger")
library("doParallel")
library("vip")
library("skimr")
library("corrplot")
library("ggridges")
library("forcats")
library("vip")
library("bonsai")
library("lightgbm")
library("xgboost")
library("ggplot2")

require("lubridate")

```

## Load Train and Test Data
```{r}
load("/home/angelo/Documents/Uni/Courses/Machine Learning & Algorithms/group_assignment/data/bookings_train.RData")
load("/home/angelo/Documents/Uni/Courses/Machine Learning & Algorithms/group_assignment/data/bookings_test_solutions.RData")
```


## Feature Engineering on Train- & Test data
```{r}
# Create Day of Week: Train
tst <- c(bookings_train$arrival_date_month)
bookings_train$arrival_date_month_numb <- match(tst,month.name)

bookings_train$date_col <- as.Date(ISOdate(year = bookings_train$arrival_date_year, month = bookings_train$arrival_date_month_numb, day = bookings_train$arrival_date_day_of_month))

bookings_train$arrival_date_day_of_week <- wday(bookings_train$date_col)

bookings_train$arrival_date_day_of_week <- as.factor(bookings_train$arrival_date_day_of_week)



# Create Day of Week: Test
tst <- c(bookings_test_solutions$arrival_date_month)
bookings_test_solutions$arrival_date_month_numb <- match(tst,month.name)

bookings_test_solutions$date_col <- as.Date(ISOdate(year = bookings_test_solutions$arrival_date_year, month = bookings_test_solutions$arrival_date_month_numb, day = bookings_test_solutions$arrival_date_day_of_month))

bookings_test_solutions$arrival_date_day_of_week <- wday(bookings_test_solutions$date_col)

bookings_test_solutions$arrival_date_day_of_week <- as.factor(bookings_test_solutions$arrival_date_day_of_week)



# Did Customer get assigned their reserved Room?: Train
bookings_train$got_reserved_room <- as.numeric(bookings_train$reserved_room_type == bookings_train$assigned_room_type)

bookings_train$got_reserved_room <- as.factor(bookings_train$got_reserved_room)



# Did Customer get assigned their reserved Room?: Test
bookings_test_solutions$got_reserved_room <- as.numeric(bookings_test_solutions$reserved_room_type == bookings_test_solutions$assigned_room_type)

bookings_test_solutions$got_reserved_room <- as.factor(bookings_test_solutions$got_reserved_room)




# Total Visitors: Train
bookings_train$total_visitors <- bookings_train$children + bookings_train$adults + bookings_train$babies


# Total Visitors: Test
bookings_test_solutions$total_visitors <- bookings_test_solutions$children + bookings_test_solutions$adults + bookings_test_solutions$babies
```


## Data Cleaning
```{r}
# Set Country NULL values to NA: Train
bookings_train$country <- ifelse(bookings_train$country == "NULL", NA, bookings_train$country)

# convert to factor: Train 
bookings_train$arrival_date_year <- as.factor(bookings_train$arrival_date_year)
bookings_train$arrival_date_month <- as.factor(bookings_train$arrival_date_month)
bookings_train$arrival_date_week_number <- as.factor(bookings_train$arrival_date_week_number)
bookings_train$arrival_date_day_of_month <- as.factor(bookings_train$arrival_date_day_of_month)
bookings_train$reserved_room_type <- as.factor(bookings_train$reserved_room_type)
bookings_train$country <- as.factor(bookings_train$country)

bookings_train$arrival_date_day_of_week <- as.numeric(bookings_train$arrival_date_day_of_week)
bookings_train$arrival_date_month_numb <- as.numeric(bookings_train$arrival_date_month_numb)
bookings_train$arrival_date_week_number <- as.numeric(bookings_train$arrival_date_week_number)

bookings_train$country <- fct_lump_min(as.factor(bookings_train$country), min=200, other_level = "Other")



# Set Country NULL values to NA: Test
bookings_test_solutions$country <- ifelse(bookings_test_solutions$country == "NULL", NA, bookings_test_solutions$country)

# convert to factor: Test
bookings_test_solutions$arrival_date_year <- as.factor(bookings_test_solutions$arrival_date_year)
bookings_test_solutions$arrival_date_month <- as.factor(bookings_test_solutions$arrival_date_month)
bookings_test_solutions$arrival_date_week_number <- as.factor(bookings_test_solutions$arrival_date_week_number)
bookings_test_solutions$arrival_date_day_of_month <- as.factor(bookings_test_solutions$arrival_date_day_of_month)
bookings_test_solutions$reserved_room_type <- as.factor(bookings_test_solutions$reserved_room_type)
bookings_test_solutions$country <- as.factor(bookings_test_solutions$country)

bookings_test_solutions$arrival_date_day_of_week <- as.numeric(bookings_test_solutions$arrival_date_day_of_week)
bookings_test_solutions$arrival_date_month_numb <- as.numeric(bookings_test_solutions$arrival_date_month_numb)
bookings_test_solutions$arrival_date_week_number <- as.numeric(bookings_test_solutions$arrival_date_week_number)

bookings_test_solutions$country <- fct_lump_min(as.factor(bookings_test_solutions$country), min=200, other_level = "Other")
```


## Remove Seemingly wrong Observations (TRAIN SET ONLY!!! -- DO NOT TOUCH TEST SET)
```{r}
# remove 0 visits
bookings_train <- bookings_train %>% 
  filter(!(stays_in_weekend_nights == 0 & stays_in_week_nights == 0)) %>% 
  filter(adults != 0) %>% 
  filter(!(adr < 0))

```


## Define Recipe
```{r}
recipe_prelim <- recipe(is_cancelled ~ ., data = bookings_train) |> 
    step_novel('assigned_room_type') |>
  update_role( "date_col", "arrival_date_month", "babies",  "arrival_date_day_of_month", "days_in_waiting_list", new_role = "metadata") |>
  step_harmonic('arrival_date_week_number',frequency=1,cycle_size=53, role='predictor') |>
  step_harmonic('arrival_date_month_numb',frequency=1,cycle_size=12, role='predictor') |>   
  step_harmonic('arrival_date_day_of_week',frequency=1,cycle_size=7, role='predictor') |>   
  step_impute_mode("country") |>
  step_normalize(all_numeric_predictors())|>
  step_dummy(all_nominal_predictors())
```


## Define LightGBM
```{r}
lgbm_model <- boost_tree(
  mtry = 22, 
  trees = 3600, 
  min_n = 15, 
  tree_depth = 11,
  learn_rate = 0.019,
  stop_iter = 300)|>
  set_mode("classification") |>
set_engine("lightgbm")
```


## Define Random Forest
```{r}
rf_model <- rand_forest(mtry = 11, 
                        trees = 500) |>
  set_mode("classification") |>
  set_engine("ranger", importance = "permutation")
```


## Define XGBoost
```{r}
xgb_model <- 
  boost_tree(trees = 2703, 
             tree_depth = 11, 
             learn_rate = 0.021,
             mtry = 20, 
             min_n = 12, 
             stop_iter = 400) |>
  set_mode("classification") |>
set_engine("xgboost")
```

## Define Linear Model
```{r}
lr_model <- logistic_reg(mode = "classification", 
                       engine = "glm", 
                       penalty = NULL, 
                       mixture = NULL)
```


## Workflow LightGBM
```{r}
lgbm_wf <- workflow() |>
  add_recipe(recipe_prelim) |>
  add_model(lgbm_model)
```

## Workflow Random Forest
```{r}
rf_wf <- workflow() |>
  add_recipe(recipe_prelim) |>
  add_model(rf_model)
```

## Workflow xGBoost
```{r}
xgb_wf <- workflow() |>
  add_recipe(recipe_prelim) |>
  add_model(xgb_model)
```

## Workflow Logistic Regression Model
```{r}
lr_wf <- workflow() |>
  add_recipe(recipe_prelim) |>
  add_model(lr_model)
```

## Fit LightGBM
```{r}
set.seed(42)

lgbm_wf_fit <- lgbm_wf %>% 
  fit(data = bookings_train)
```

## Fit Random Forest
```{r}
set.seed(42)

rf_wf_fit <- rf_wf %>% 
  fit(data = bookings_train)
```

## Fit XGBoost
```{r}
set.seed(42)

xgb_wf_fit <- xgb_wf %>% 
  fit(data = bookings_train)
```

## Fit Logisitc Regression Model
```{r}
set.seed(42)

lr_wf_fit <- lr_wf %>% 
  fit(data = bookings_train)
```


## Define Evaluation Metrics
```{r}
eval_metrics <- metric_set(accuracy, bal_accuracy, recall, precision, f_meas, specificity)
```


## LightGBM: Predict on the Test Set
```{r}
lgbm_results <- bookings_test_solutions %>% select(is_cancelled) %>% 
  bind_cols(lgbm_wf_fit %>% 
              predict(new_data = bookings_test_solutions)) %>% 
  bind_cols(lgbm_wf_fit %>% 
              predict(new_data = bookings_test_solutions, type = "prob"))

```

## Random Forest: Predict on the Test Set
```{r}
rf_results <- bookings_test_solutions %>% select(is_cancelled) %>% 
  bind_cols(rf_wf_fit %>% 
              predict(new_data = bookings_test_solutions)) %>% 
  bind_cols(rf_wf_fit %>% 
              predict(new_data = bookings_test_solutions, type = "prob"))

```

## XGBoost: Predict on the Test Set
```{r}
xgb_results <- bookings_test_solutions %>% select(is_cancelled) %>% 
  bind_cols(xgb_wf_fit %>% 
              predict(new_data = bookings_test_solutions)) %>% 
  bind_cols(xgb_wf_fit %>% 
              predict(new_data = bookings_test_solutions, type = "prob"))

```


## Logistic Regression Model: Predict on the Test Set
```{r}
lr_results <- bookings_test_solutions %>% select(is_cancelled) %>% 
  bind_cols(lr_wf_fit %>% 
              predict(new_data = bookings_test_solutions)) %>% 
  bind_cols(lr_wf_fit %>% 
              predict(new_data = bookings_test_solutions, type = "prob"))

```


# LightGBM: Evaluation Metrics
```{r}
eval_metrics(data = lgbm_results, truth = is_cancelled, estimate = .pred_class)
```

# Random Forest: Evaluation Metrics
```{r}
eval_metrics(data = rf_results, truth = is_cancelled, estimate = .pred_class)
```

# XGBoost: Evaluation Metrics
```{r}
eval_metrics(data = xgb_results, truth = is_cancelled, estimate = .pred_class)
```

# Logistic Model: Evaluation Metrics
```{r}
eval_metrics(data = lr_results, truth = is_cancelled, estimate = .pred_class)
```
## Feature Importances
```{r}
xgb_vi <- xgb_wf_fit %>%
  fit(data = bookings_train) %>%
  pull_workflow_fit() %>%
  vi()

xgb_vi %>%
  mutate(Variable = fct_reorder(Variable, Importance)) %>%
  slice_head(n = 12) %>% 
  ggplot( aes(x=Variable, y=Importance*100)) +
  geom_bar(stat="identity", fill="#f68060", alpha=.6, width=.4) +
  coord_flip() +
  labs(title = "XGBoost Node Purity Gain",
       y="Percentage of Total Gain")
theme_bw()
```


```{r}
rf_vi <- rf_wf_fit %>%
  fit(data = bookings_train) %>%
  pull_workflow_fit() %>%
  vi()

rf_vi %>% 
  mutate(Variable = fct_reorder(Variable, Importance)) %>%
  slice_head(n = 12) %>% 
  ggplot( aes(x=Variable, y=Importance*100)) +
  geom_bar(stat="identity", fill="#f68060", alpha=.6, width=.4) +
  coord_flip() +
  labs(title = "Random Forest Permutation Variable Importance",
       y="Percentage Increase in Error")
theme_bw()
```
## Tidymodels cannot extract feature importances for LightGBM
## Retrain the exact model with the LightGBM package to obtain feature importances
```{r}
set.seed(42)

bookings_train_prepped <- recipe_prelim %>% prep(bookings_train) %>% bake(bookings_train)

bookings_train_pred <- bookings_train_prepped %>%
  select(-is_cancelled)

bookings_train_outcome <- bookings_train_prepped %>% 
  select(is_cancelled) %>% 
  mutate(is_cancelled = ifelse(is_cancelled == 'yes', 1, 0))

train_x <- as.matrix(bookings_train_pred)
train_y <- as.matrix(bookings_train_outcome)

dtrain <- lgb.Dataset(train_x, label = train_y)


lgbm_model <- boost_tree(
  mtry = 9, 
  trees = 2124, 
  min_n = 4, 
  tree_depth = 10,
  learn_rate = 0.009549070,
  stop_iter = 300)|>
  set_mode("classification") |>
set_engine("lightgbm")



params <- list(
  objective = "binary"
  , learning_rate = 0.009549070
  , max_depth = 10L
  , min_data_in_leaf = 4L
  , min_sum_hessian_in_leaf = 1.0
  , feature_fraction = 9/ncol(bookings_train_pred)
)

model <- lgb.train(
    params = params
    , data = dtrain
    , num_iterations = 2124L
)

tree_imp <- lgb.importance(model, percentage = TRUE)
tree_imp
```

## Visualize Feature Importance for LGBM
```{r}
# Reorder following the value of another column:
tree_imp %>%
  mutate(Feature = fct_reorder(Feature, Gain)) %>%
  slice_head(n = 12) %>% 
  ggplot( aes(x=Feature, y=Gain*100)) +
  geom_bar(stat="identity", fill="#f68060", alpha=.6, width=.4) +
  geom_point(aes(x=Feature, y=Frequency*100), alpha=.6, size=3) +
  coord_flip() +
  labs(title = "LightGBM Node Purity Gain (bar) and Split Frequency (point)",
       y="Percentage of Total")
theme_bw()
```

## Plot ROC-curves for all models
```{r}
lgbm_roc <- roc_curve(lgbm_results, .pred_yes, truth = is_cancelled)
xgb_roc <- roc_curve(xgb_results, .pred_yes, truth = is_cancelled)
rf_roc <- roc_curve(rf_results, .pred_yes, truth = is_cancelled)
lr_roc <- roc_curve(lr_results, .pred_yes, truth = is_cancelled)

lgbm_auc <- roc_auc(lgbm_results, .pred_yes, truth = is_cancelled)
xgb_auc <- roc_auc(xgb_results, .pred_yes, truth = is_cancelled)
rf_auc <- roc_auc(rf_results, .pred_yes, truth = is_cancelled)
lr_auc <- roc_auc(lr_results, .pred_yes, truth = is_cancelled)


colors <- c("LightGBM"="blue", "XGBoost"="darkred", "Random Forest"="darkgreen",
            "Log. Reg."="darkorange")

ggplot(lgbm_roc, aes(x = 1 - specificity, y = sensitivity, color='LightGBM')) +
  geom_path(alpha=.5, size=1) +
  geom_path(data = xgb_roc, aes(x = 1 - specificity, y = sensitivity, color='XGBoost'), alpha=.5, size=1) +
  geom_path(data = rf_roc, aes(x = 1 - specificity, y = sensitivity, color='Random Forest'), alpha=.5, size=1) +
  geom_path(data = lr_roc, aes(x = 1 - specificity, y = sensitivity, color='Log. Reg.'), alpha=.5, size=1) +
  geom_abline(lty = 3) +
  labs(title="ROC curve", color="Legend") +
  coord_equal() +
  scale_color_manual(values = colors)
```

## Plot PR-curves for all models
```{r}
lgbm_pr <- pr_curve(lgbm_results, .pred_yes, truth = is_cancelled)
xgb_pr <- pr_curve(xgb_results, .pred_yes, truth = is_cancelled)
rf_pr <- pr_curve(rf_results, .pred_yes, truth = is_cancelled)
lr_pr <- pr_curve(lr_results, .pred_yes, truth = is_cancelled)

ggplot(lgbm_pr, aes(x = recall, y = precision, color='LightGBM')) +
  geom_path(alpha=.5, size=1) +
  geom_path(data = xgb_pr, aes(x = recall, y = precision, color='XGBoost'), alpha=.5, size=1) +
  geom_path(data = rf_pr, aes(x = recall, y = precision, color='Random Forest'), alpha=.5, size=1) +
  geom_path(data = lr_pr, aes(x = recall, y = precision, color='Log. Reg.'), alpha=.5, size=1) +
  labs(title="Precision-Recall Curve", color="Legend") +
  coord_equal() +
  scale_color_manual(values = colors)
```
## Print AUC scores
```{r}
print(lgbm_auc)
print(rf_auc)
print(xgb_auc)
print(lr_auc)
```


