---
title: "Random Forest"
author: "JeanLuc"
date: "2022-12-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Imports
```{r}
library("tidymodels")
library("themis")
library("knitr")
library("ranger")
library("doParallel")
library("vip")
library("skimr")
library("corrplot")
library("ggridges")
library("forcats")
library("vip")
library("bonsai")
library("lightgbm")
library("xgboost")
library("ggplot2")
library("tictoc")

require("lubridate")
```

## Load Train and Test Data
```{r}
load("D:/Universiteit/R/GroupAssignmentML2022/bookings_train.RData")
load("D:/Universiteit/R/GroupAssignmentML2022/bookings_test_solutions.RData")
```


## Feature Engineering on Train- & Test data
```{r}
# Create Day of Week: Train
tst <- c(bookings_train$arrival_date_month)
bookings_train$arrival_date_month_numb <- match(tst,month.name)

bookings_train$date_col <- as.Date(ISOdate(year = bookings_train$arrival_date_year, month = bookings_train$arrival_date_month_numb, day = bookings_train$arrival_date_day_of_month))

bookings_train$arrival_date_day_of_week <- wday(bookings_train$date_col)

bookings_train$arrival_date_day_of_week <- as.factor(bookings_train$arrival_date_day_of_week)

# Did Customer get assigned their reserved Room?: Train
bookings_train$got_reserved_room <- as.numeric(bookings_train$reserved_room_type == bookings_train$assigned_room_type)

bookings_train$got_reserved_room <- as.factor(bookings_train$got_reserved_room)

# Total Visitors: Train
bookings_train$total_visitors <- bookings_train$children + bookings_train$adults + bookings_train$babies
```


## Data Cleaning
```{r}
# Set Country NULL values to NA: Train
bookings_train$country <- ifelse(bookings_train$country == "NULL", NA, bookings_train$country)

# convert to factor: Train 
bookings_train$arrival_date_year <- as.factor(bookings_train$arrival_date_year)
bookings_train$arrival_date_month <- as.factor(bookings_train$arrival_date_month)
bookings_train$arrival_date_week_number <- as.factor(bookings_train$arrival_date_week_number)
bookings_train$arrival_date_day_of_month <- as.factor(bookings_train$arrival_date_day_of_month)
bookings_train$reserved_room_type <- as.factor(bookings_train$reserved_room_type)
bookings_train$country <- as.factor(bookings_train$country)

bookings_train$arrival_date_day_of_week <- as.numeric(bookings_train$arrival_date_day_of_week)
bookings_train$arrival_date_month_numb <- as.numeric(bookings_train$arrival_date_month_numb)
bookings_train$arrival_date_week_number <- as.numeric(bookings_train$arrival_date_week_number)

bookings_train$country <- fct_lump_min(as.factor(bookings_train$country), min=200, other_level = "Other")
```


## Remove Seemingly wrong Observations
```{r}
# remove 0 visits
bookings_train <- bookings_train %>% 
  filter(!(stays_in_weekend_nights == 0 & stays_in_week_nights == 0)) %>% 
  filter(adults != 0) %>% 
  filter(!(adr < 0))
```


# Simple preprocsessing
```{r}
bookings_train$country <- fct_lump_min(as.factor(bookings_train$country), min=200, other_level = "Other")

# remove 0 visits
bookings_train <- bookings_train %>% 
  filter(!(stays_in_weekend_nights == 0 & stays_in_week_nights == 0)) %>% 
  filter(adults != 0)

bookings_train <- bookings_train %>% 
  filter(!(adr < 0))

bookings_train$total_visitors <- bookings_train$children + bookings_train$adults + bookings_train$babies
```

# splitting the data
```{r}
# split the data
set.seed(42)
bookings_train_split <- initial_split(data = bookings_train, prop = 0.8, 
                          strata = is_cancelled)

# I keep the train in the name for a reason: this way we can differentiate between validation and test set later on
bookings_train_train <- training(bookings_train_split)
bookings_train_test <- testing(bookings_train_split)
print(bookings_train_train |> count(is_cancelled) |> 
  mutate(prop = n / sum(n)))
print(bookings_train_test |> count(is_cancelled) |> 
  mutate(prop = n / sum(n)))

```

# Create CV-folds
```{r}
set.seed(82001)
cv_folds <- bookings_train_train |> vfold_cv(v = 5, strata = is_cancelled)
```

# Define Model
```{r}
set.seed(42)
rf_model_tune <- rand_forest(mtry = tune(), trees = 500) |>
  set_mode("classification") |>
  set_engine("ranger", importance = "permutation")
```


# Define Recipe
```{r}
recipe_prelim <- recipe(is_cancelled ~ ., data = bookings_train_train) |> 
    step_novel('assigned_room_type') |>
  update_role( "date_col", "arrival_date_month", "babies",  "arrival_date_day_of_month", "days_in_waiting_list",  new_role = "metadata") |>
  step_harmonic('arrival_date_week_number',frequency=1,cycle_size=53, role='predictor') |>
  step_harmonic('arrival_date_month_numb',frequency=1,cycle_size=12, role='predictor') |>   
  step_harmonic('arrival_date_day_of_week',frequency=1,cycle_size=7, role='predictor') |>   
  step_impute_mode("country") |>
  step_normalize(all_numeric_predictors())|>
  step_dummy(all_nominal_predictors()) 
```


# Combine Workflow
```{r}
rf_tune_wf <- workflow() |>
  add_recipe(recipe_prelim) |>
  add_model(rf_model_tune)
```


# Define Metrics
```{r}
class_metrics <- metric_set(accuracy, f_meas, precision, recall, specificity, roc_auc)
```


# Parallel Computations
```{r}
registerDoParallel()
```


# Create RandomSearch Grid and Perform Tuning
```{r}
set.seed(42)

tic()
rf_tune_res <- tune_grid(
  rf_tune_wf,
  resamples = cv_folds,
  grid = tibble(mtry = 7:11),
  metrics = class_metrics
)
toc()

show_notes(.Last.tune.result)
```

# Extract Best Values
```{r}
rf_tune_metrics <- rf_tune_res |>
  collect_metrics()
rf_tune_metrics
```

# Plot Sensitivity, Specificity
```{r}
rf_tune_res |>
  collect_metrics() |>
  filter(.metric %in% c("recall", "specificity")) |>
  ggplot(aes(x = mtry, y = mean, ymin = mean - std_err, ymax = mean + std_err, 
             colour = .metric)) +
  geom_errorbar() + 
  geom_line() +
  geom_point() +
  facet_grid(.metric ~ ., scales = "free_y") 
```

# Plot AUC, Accuracy, Kappa
```{r}
rf_tune_res |>
  collect_metrics() |>
  filter(.metric %in% c("roc_auc", "accuracy", "kap")) |>
  ggplot(aes(x = mtry, y = mean, ymin = mean - std_err, ymax = mean + std_err, 
             colour = .metric)) +
  geom_errorbar() + 
  geom_line() +
  geom_point() +
  facet_grid(.metric ~ ., scales = "free_y") 
```

# Extract Best Model
```{r}
best_acc <- select_best(rf_tune_res, "f_meas")
rf_final_wf <- finalize_workflow(rf_tune_wf, best_acc)
rf_final_wf
```

# Final fit to extract importances
```{r}
set.seed(9923)
rf_final_fit <- rf_final_wf |>
  last_fit(bookings_train_split, metrics = class_metrics)
# The results on the test set for class predictions are:
rf_final_fit |>
  collect_metrics()
```

# VIP
```{r}
rf_final_fit %>% extract_fit_parsnip() %>% vi()
rf_final_fit |> extract_fit_parsnip() |> vip(geom = "point", num_features = 40)
```






